Clustering Analysis of Mobility Data

### 2018-06-30 dokumentation/submission.tex
NN started

		\keywords{Clustering \and Rapidminer \and Cluster \and Data Mining} %TODO: maybe more
	\end{abstract}
	%
	%
	%
	\section{Introduction}
	\section{Preprocessing}
	In order to classify the given data into smaller test sets or mask different aspects, we have to perform analysis.\\
	We observe that even though we have 124979 individual lines defining a movement, there is one line defining a \texttt{NotANumber}-exception and therefore gets neglected for further usage.	\\
	We provide the \texttt{testDataGenerator} python script. Through flags and input arguments the script is able to create all test sets considered by our clustering and neural net approaches.\\
	%TODO: should this be within the paper or more in a ReadMe-file delivered with the script itself?
%	The possible flags and an explanation can be taken from \Cref{fig: testdatagenerator flags}.	
%	\begin{figure}[H]
%		\centering
%		\includegraphics[scale=0.5]{src/pic/testDataGenerator-h.PNG}
%		\caption{The possible arguments to the \texttt{testDataGenerator}}
%		\label{fig: testdatagenerator flags}
%	\end{figure}
	We observe the following distribution over the whole dataset:\\
	{\hspace*{2cm}\setlength\tabcolsep{.2cm}\begin{tabular}{c|ccccccc}
		strata &  1   &   2   &   3   &  4   &  5   &  6   & $\Sigma$ \\ \hline
		 abs   & 6963 & 52265 & 49404 & 8772 & 5536 & 2038 &  124978  \\
		  \%   & 5.57 & 41.82 & 39.53 & 7.02 & 4.43 & 1.63 &   100
	\end{tabular}}\\
	We observe that there is an upper bound on equal distribution through strata 6. It has at most 2038 individual elements.

@@

	\subsection{Classification}
	\subsection{Neural Net}
	Also we have a max. of 595 persons for strata 6 to have an equally distributed test set.\\	
	All using the vector data\\

	We consider 3 neural nets $\mathcal{N}_1,\mathcal{N}_2$ and $\mathcal{N}_3$, all having 4 hidden layers, 50 epochs and 10 iterations.	
	As an example of other strata aggregation we combine the stratas 1--2, 3--4 and 5--6 together and call them $\mathcal{N}_i^\star$, for $i \in \{5,10,20\}$. For that we take an equal distribution of all original stratas and map them correspondingly to the new stratas. 	
	\setlength\tabcolsep{.2cm}
	\begin{figure}[H]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		                         &   \#    &        & \multicolumn{3}{c|}{Set size} \\
		          Name           & Neurons &   AG   &  100  &  200  &      595      \\ \hline
		    $\mathcal{N}_5$      &    5    & \xmark & 60.03 & 59.92 &     60.18     \\
		 $\mathcal{N}_5^\star$   &    5    & \cmark & 87.6  & 89.7  &     71.05     \\
		   $\mathcal{N}_{10}$    &   10    & \xmark & 75.83 & 73.54 &     69.56     \\
		$\mathcal{N}_{10}^\star$ &   10    & \cmark & 92.93 & 93.48 &     74.58     \\		
		%		$\mathcal{N}_{10}^\star$ &   10    & \cmark & 88.33 {\small $\pm$7.49} & 90.67{\small $\pm$2.81} & 92.14 {\small $\pm$ 2.59} \\
		   $\mathcal{N}_{20}$    &   20    & \xmark & 75.45 & 71.14 &     61.87     \\
		$\mathcal{N}_{20}^\star$ &   20    & \cmark & 92.87 & 94.4  &     78.32     \\ \hline
	\end{tabular}
	\caption{The accuracy values of the neural nets. (See excel-spreadsheet)}
	\label{tab: nn-accuracy}
	% mittels deep-learning-vector-average
	\end{figure}

If we take 50 neurons per layer we have $14 \cdot 50^4 \cdot 6 \approxeq 525.000.000$ synapses for which the input data set would be to small to have sufficient training.\\

The greater the population, the more the borders between the stratas blur.

>>>>

		\keywords{Clustering \and Rapidminer \and Cluster \and Data Mining} %TODO: maybe more
	\end{abstract}
	%
	%
	%
	\section{Introduction}
	\section{Preprocessing}\label{sec: proprocessing}
	In order to classify the given data into smaller test sets or mask different aspects, we have to perform analysis.\\
	We observe that even though we have 124979 individual lines defining a movement, there is one line defining a \texttt{NotANumber}-exception and therefore gets neglected for further usage.	\\
	We provide the \texttt{testDataGenerator} python script. Through flags and input arguments the script is able to create all test sets considered by our clustering and neural net approaches.\\
	%TODO: should this be within the paper or more in a ReadMe-file delivered with the script itself?
%	The possible flags and an explanation can be taken from \Cref{fig: testdatagenerator flags}.	
%	\begin{figure}[H]
%		\centering
%		\includegraphics[scale=0.5]{src/pic/testDataGenerator-h.PNG}
%		\caption{The possible arguments to the \texttt{testDataGenerator}}
%		\label{fig: testdatagenerator flags}
%	\end{figure}
	We observe the following distribution over the whole dataset:\\
	{\hspace*{2cm}\setlength\tabcolsep{.2cm}\begin{tabular}{c|ccccccc}
		strata &  1   &   2   &   3   &  4   &  5   &  6   & $\Sigma$ \\ \hline
		 abs   & 6963 & 52265 & 49404 & 8772 & 5536 & 2038 &  124978  \\
		  \%   & 5.57 & 41.82 & 39.53 & 7.02 & 4.43 & 1.63 &   100
	\end{tabular}}\\
	We observe that there is an upper bound on equal distribution through strata 6. It has at most 2038 individual elements.

@@

	\subsection{Classification}
	\subsection{Neural Net}
	For all the neural net computations done we considered person vector data sets of different sizes (c.f. \Cref{subsec: person vector data}).\\
	We do this, because results on the normal datasets had an unacceptable performance. An example is given in \Cref{fig: NN without vector}.	
	\begin{figure}
		\centering
		\includegraphics[scale = 0.4]{src/pic/NN_without_vector.png}
		\caption{An example of a neural net trained without person vector data.}
		\label{fig: NN without vector}
	\end{figure}

	In the following we consider 3 neural nets $\mathcal{N}_1,\mathcal{N}_2$ and $\mathcal{N}_3$, all having 4 hidden layers, 50 epochs and 10 iterations.	
	As an example of other strata aggregation we combine the stratas 1--2, 3--4 and 5--6 together and call them $\mathcal{N}_i^\star$, for $i \in \{5,10,20\}$. This builds a superset of the original stratas and since the stratas themselves are logically connected this task should be easier to fulfill.\\
	The sets are provided by the \texttt{testDataGenerator} from \Cref{sec: proprocessing}.
	\setlength\tabcolsep{.2cm}
	\begin{figure}[H]
	\centering
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		                         &   \#    &        & \multicolumn{3}{c|}{Set size} \\
		          Name           & Neurons &   AG   &  100  &  200  &      595      \\ \hline
		    $\mathcal{N}_5$      &    5    & \xmark & 60.03 & 59.92 &     60.18     \\
		 $\mathcal{N}_5^\star$   &    5    & \cmark & 87.6  & 89.7  &     71.05     \\
		   $\mathcal{N}_{10}$    &   10    & \xmark & 75.83 & 73.54 &     69.56     \\
		$\mathcal{N}_{10}^\star$ &   10    & \cmark & 92.93 & 93.48 &     74.58     \\		
		%		$\mathcal{N}_{10}^\star$ &   10    & \cmark & 88.33 {\small $\pm$7.49} & 90.67{\small $\pm$2.81} & 92.14 {\small $\pm$ 2.59} \\
		   $\mathcal{N}_{20}$    &   20    & \xmark & 75.45 & 71.14 &     61.87     \\
		$\mathcal{N}_{20}^\star$ &   20    & \cmark & 92.87 & 94.4  &     78.32     \\ \hline
	\end{tabular}
	\caption{The accuracy values of the neural nets. (See excel-spreadsheet)}
	\label{tab: nn-accuracy}
	% mittels deep-learning-vector-average
	\end{figure}

	For each we performed 5 independent runs and take an average over those accuracy values in order to have a sophisticated statement.\\

	The size of larger nets in terms of neurons is counter-productive, since if we take 50 neurons per layer we have $14 \cdot 50^4 \cdot 6 \approxeq 525.000.000$ synapses for which the input data set would be to small to have sufficient training.\\

	%TODO: what can we oberve?
%	The greater the population, the more the borders between the stratas blur.
